Towards End-user Web Scraping For Customization

### 2021-02-14 paper.tex
add page numbers

@@

Many end-user web scraping and macro systems allow users to
\emph{create} programs by demonstration but do not offer a way to
\emph{edit} them by demonstration. In Rousillon \citep{chasins2018}, a
web scraping program created by demonstration can only be edited through
a high-level, block-based programming language called Helena
\citep{zotero-51}. Helena supports adding control flow logic
(conditional execution, wait times etc) which is invaluable for
automating access to websites. However, it does not support extending
the web scraping code to add new columns after the demonstration or
repairing it to provide new selectors if the website changes. In
Vegemite \citep{lin2009}, a web automation program created through
demonstration can only be edited by editing the text-based
representation of the automtation. In fact, only the automation script
that works on the scraped website data can be edited. If a user needs to
add a new column or repair an exisiting one in the table, they need to
re-demonstrate the columns and then re-run the automation script. One
exception to point out is import.io {[}zotero-77{]} which allows users
to add new columns by demonstration and delete columns and
re-demonstrate them which could serve the purpose of repair.

>>>>

\settopmatter{printfolios=true}

@@

Many end-user web scraping and macro systems allow users to
\emph{create} programs by demonstration but do not offer a way to
\emph{edit} them by demonstration. In Rousillon \citep{chasins2018}, a
web scraping program created by demonstration can only be edited through
a high-level, block-based programming language called Helena
\citep{zotero-51}. Helena supports adding control flow logic
(conditional execution, wait times etc) which is invaluable for
automating access to websites. However, it does not support extending
the web scraping code to add new columns after the demonstration or
repairing it to provide new selectors if the website changes. In
Vegemite \citep{lin2009}, a web automation program created through
demonstration can only be edited by editing the text-based
representation of the automtation. In fact, only the automation script
that works on the scraped website data can be edited. If a user needs to
add a new column or repair an exisiting one in the table, they need to
re-demonstrate the columns and then re-run the automation script. One
exception to point out is import.io \citep{zotero-77} which allows users
to add new columns by demonstration and delete columns and
re-demonstrate them which could serve the purpose of repair.
